A pipeline to analyse time-course gene expression data

### 2019-05-14 manuscript.tex
Deploy NelleV/2019timecourse-rnaseq-pipeline to github.com/NelleV/2019timecourse-rnaseq-pipeline.git:gh-pages

\textbf{EAP: General comment. Your function names are incredibly long compared to standard functions. Also, will want to get rid of \texttt{moanin::} in front of functions. It's more precise, but an average user doesn't ever experience the \texttt{::} command; usually just package creaters. }

@@

\CommentTok{# Define contrast   }
\NormalTok{contrasts =}\StringTok{ }\KeywordTok{c}\NormalTok{(}\StringTok{"M.0-VL.0"}\NormalTok{,}
          \StringTok{"M.3-VL.3"}\NormalTok{,}
          \StringTok{"M.6-VL.6"}\NormalTok{,}
          \StringTok{"M.9-VL.9"}\NormalTok{,}
          \StringTok{"M.12-VL.12"}\NormalTok{,}
          \StringTok{"M.18-VL.18"}\NormalTok{,}
          \StringTok{"M.24-VL.24"}\NormalTok{,}
          \StringTok{"M.30-VL.30"}\NormalTok{,}
          \StringTok{"M.36-VL.36"}\NormalTok{,}
          \StringTok{"M.48-VL.48"}\NormalTok{,}
          \StringTok{"M.60-VL.60"}\NormalTok{,}
          \StringTok{"M.72-VL.72"}\NormalTok{,}
          \StringTok{"M.120-VL.120"}\NormalTok{,}
          \StringTok{"M.168-VL.168"}\NormalTok{)}
\NormalTok{weekly_de_analysis =}\StringTok{  }\NormalTok{moanin}\OperatorTok{::}\KeywordTok{weekly_differential_expression_analysis}\NormalTok{(}
\NormalTok{     data, splines_model, contrasts,}
     \DataTypeTok{use_voom_weights=}\OtherTok{FALSE}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

@@

\CommentTok{# The function takes the data (data.frame or named matrix), the meta data}
\CommentTok{# (data.frame containing a timepoint and group column, the first corresponding}
\CommentTok{#<c2><a0>to the time-course information, the latter corresponding to the}
\CommentTok{# treatment).}
\NormalTok{pvalues =}\StringTok{ }\NormalTok{moanin}\OperatorTok{::}\KeywordTok{timecourse_differential_expression_analysis}\NormalTok{(}
\NormalTok{    data, splines_model, contrasts)}
\NormalTok{qvalues =}\StringTok{ }\KeywordTok{apply}\NormalTok{(pvalues, }\DecValTok{2}\NormalTok{, stats}\OperatorTok{::}\NormalTok{p.adjust)}
\end{Highlighting}
\end{Shaded}

>>>>

\textbf{EAP: General comment. Your function names are incredibly long compared to
standard functions. Also, will want to get rid of \texttt{moanin::} in front of
functions. It's more precise, but an average user doesn't ever experience the
\texttt{::} command; usually just package creaters.}

@@

\CommentTok{# Define contrast   }
\NormalTok{contrasts =}\StringTok{ }\KeywordTok{c}\NormalTok{(}\StringTok{"M.0-VL.0"}\NormalTok{,}
          \StringTok{"M.3-VL.3"}\NormalTok{,}
          \StringTok{"M.6-VL.6"}\NormalTok{,}
          \StringTok{"M.9-VL.9"}\NormalTok{,}
          \StringTok{"M.12-VL.12"}\NormalTok{,}
          \StringTok{"M.18-VL.18"}\NormalTok{,}
          \StringTok{"M.24-VL.24"}\NormalTok{,}
          \StringTok{"M.30-VL.30"}\NormalTok{,}
          \StringTok{"M.36-VL.36"}\NormalTok{,}
          \StringTok{"M.48-VL.48"}\NormalTok{,}
          \StringTok{"M.60-VL.60"}\NormalTok{,}
          \StringTok{"M.72-VL.72"}\NormalTok{,}
          \StringTok{"M.120-VL.120"}\NormalTok{,}
          \StringTok{"M.168-VL.168"}\NormalTok{)}
\NormalTok{weekly_de_analysis =}\StringTok{  }\NormalTok{moanin}\OperatorTok{::}\KeywordTok{DE_timepoints}\NormalTok{(}
\NormalTok{     data, splines_model, contrasts,}
     \DataTypeTok{use_voom_weights=}\OtherTok{FALSE}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

@@

\CommentTok{# The function takes the data (data.frame or named matrix), the meta data}
\CommentTok{# (data.frame containing a timepoint and group column, the first corresponding}
\CommentTok{#<c2><a0>to the time-course information, the latter corresponding to the}
\CommentTok{# treatment).}
\NormalTok{pvalues =}\StringTok{ }\NormalTok{moanin}\OperatorTok{::}\KeywordTok{DE_timecourse}\NormalTok{(}
\NormalTok{    data, splines_model, contrasts,}
    \DataTypeTok{use_voom_weights=}\OtherTok{FALSE}\NormalTok{)}
\NormalTok{qvalues =}\StringTok{ }\KeywordTok{apply}\NormalTok{(pvalues, }\DecValTok{2}\NormalTok{, stats}\OperatorTok{::}\NormalTok{p.adjust)}
\end{Highlighting}
\end{Shaded}
